TUD Datasets: A collection of benchmark datasets for learning with graphs

### 2020-03-26 main.tex
MC.

The papers~\cite{Fey+2019,Err+2019,Dwi+2020} evalute GNNs using a unified evaluation procedure, however, both only use small scale datasets. Recently, \url{ogb.stanford.edu} launchend, however the provided datasets for graph classification focus on chemistry applications.

@@

>>>>

The papers~\cite{Fey+2019,Err+2019,Dwi+2020} evalute GNNs using a unified evaluation procedure, however, both only use small scale datasets. Recently, \url{ogb.stanford.edu} launchend, however the provided datasets for graph classification focus on chemistry applications, and the number is quite limited at this point.

@@

The \textsc{Tud dataset} contain over 150 datasets provided at \url{graphlearning.io}.
